MITM: Logging a Bluetooth Keyboard

### 2013-03-15 final_paper/paper.tex
added table of encodings

Hidclient allows the user to forward from any input device the user specifies and that the computer recognizes as a valid input. Since the victim's Bluetooth keyboard is connected to the attacker already, hidclient recognizes the keyboard as an input source. This means the attacker's keyboard is free for typing and will not appear on the victim's screen. The keystrokes are forwarded on to the victim with minimal delay.

\subsection{Keylogging}
We used python script based on findings of \cite{chopper}

@@

\subsection{Hardware and Software}
For this attack, we wanted to test several versions of Bluetooth as well as different Operating Systems to determine how effective the attack is against different hardware and software. The following are the devices we used for the attack:\\
\textbf{Keyboard:} we used a basic Bluetooth keyboard that uses Bluetooth V3.0+EDR (Enhanced Data Rate (EDR), an optional speed-up of data transfer)\\
\textbf{Attack Device:} Lenovo Thinkpad z61t laptop running Ubuntu 12.04 with Bluetooth 2.0+EDR\\
\textbf{Victim Devices:} we attacked a mid-2012 Apple Macbook Air running Ubuntu 12.10 via VirtualBox with
Bluetooh 4.0 card and a desktop PC with a Bluetooth dongle, running Ubuntu 12.04 and Bluetooth 4.0.

@@

\begin{enumerate}
\item Stay out of discoverable mode as much as possible. This way any attacker would need special hardware to perform any kind of fancy attack and take much longer to actually find the keyboards Bluetooth address.
\item Keyboards should require a PIN to pair every time. Keyboards potentionally handle much more sensitive data than a device such as a Bluetooth receiver.
\item Bluetooth manager applications should be smarter. If they notice a previously paired keyboard or device with the same name that has a different Bluetooth address that might warrant a red flag to be displayed to the user.
\end{enumerate}

@@

\begin{enumerate}
\item Implement the entire attack. Including the denial-of-service and pairing without the users knowledge.
\item Get Ubertooth and succesfully use it to choose victims without having to have prior knowledge about the victim and the keyboard.
\item Implement the entire attack in a single C/C++ application. This would make testing and debugging much easier to perform. Instead of requiring several seperate tools combined together.
\item Acquire passwords!
\end{enumerate}

>>>>

Hidclient allows the user to forward from any input device the user specifies and that the computer recognizes as a valid input. Since the victim's Bluetooth keyboard is connected to the attacker already, hidclient recognizes the keyboard as an input source. This means the attacker's keyboard is free for typing and will not appear on the victim's screen. The keystrokes are forwarded on to the victim with minimal delay. 
\begin{table}
\begin{tabular}{|c|c|}
\hline
Key Value & hcidump Encoding\\\hline
A&0x04\\
B&0x05\\
C&0x06\\ 
D&0x07\\
E&0x08\\
F&0x09\\
G&0x0A\\
H&0x0B\\
I&0x0C\\
J&0x0D\\
K&0x0E\\
L&0x0F\\
M&0x10\\
N&0x11\\
O&0x12\\
P&0x13\\
Q&0x14\\
R&0x15\\
S&0x16\\
T&0x17\\
U&0x18\\
V&0x19\\
W&0x1A\\
X&0x1B\\
Y&0x1C\\
Z&0x1D\\
1&0x1E\\
2&0x1F\\
3&0x20\\
4&0x21\\
5&0x22\\
6&0x23\\
7&0x24\\
8&0x25\\
9&0x26\\\hline
\end{tabular}
\begin{center}
\caption{Keys to Encoded Value from \texttt{hcidump}}
\end{center}
\label{table1}
\end{table}
\subsection{Keylogging}
In order to get the data from the Bluetooth packets, we needed to dump the data in a way that it was retrievable either during the attack or after the fact. We considered several packet logger programs including Kismet \cite{kismet}, Wireshark \cite{wireshark}, and Mac OSX's Bluetooth Packet Logger. There were a few concerns with these tools: Kismet did not have support without the Ubertooth hardware, and so we did not choose to use this approach; Wireshark has bluetooth support, but the data is difficult to extract, except through log files; and the OSX Packet Logger was only available on OSX, which meant we were unable to use Linux BlueZ utilities.

A simple solution is to use a BlueZ dumping tool called \texttt{hcidump} which provided the option to dump the data in hexidecimal form. Since the data coming from the keyboard was unencrypted, this data could be easily extracted from the dump during or after the attack.

To extract the data, we wrote a Python script based on findings of a Chinese blogger, alias Chopper \cite{chopper}. Chopper noted that data coming out of \texttt{hcidump} was not encrypted but encoded such that characters on the keyboard were given hexidecimal values that did not correspond to their ASCII values, as shown in Figure 1. However, decoding the output proved quite simple, and can be determined by simply pressing a key and looking at the corresponding \texttt{hcidump} output. We decoded some of them in our Python script to show a proof of concept, the values of which are shown in Table 1.

@@

\subsection{Hardware and Software}
For this attack, we wanted to test several versions of Bluetooth as well as different Operating Systems to determine how effective the attack is against different hardware and software. The following are the devices we used for the attack:

\textbf{Keyboard:} we used a basic Bluetooth keyboard that uses Bluetooth V3.0+EDR (Enhanced Data Rate (EDR), an optional speed-up of data transfer)\\
\textbf{Attack Device:} Lenovo Thinkpad z61t laptop running Ubuntu 12.04 with Bluetooth 2.0+EDR\\
\textbf{Victim Devices:} we attacked a mid-2012 Apple Macbook Air running Ubuntu 12.10 via VirtualBox with
Bluetooh 4.0 card and a desktop PC with a Bluetooth dongle, running Ubuntu 12.04 and Bluetooth 4.0.

@@

\begin{enumerate}
\item Stay out of discoverable mode as much as possible. This way any attacker would need special hardware to perform any kind of fancy attack and take much longer to actually find the keyboards Bluetooth address.
\item Keyboards should require a PIN to pair every time. Keyboards potentially handle much more sensitive data than a device such as a Bluetooth receiver.
\item Bluetooth manager applications should be smarter. If they notice a previously paired keyboard or device with the same name that has a different Bluetooth address that might warrant a red flag to be displayed to the user.
\end{enumerate}

@@

\begin{enumerate}
\item Implement the entire attack. Including the denial-of-service and pairing without the users knowledge.
\item Get Ubertooth and successfully use it to choose victims without having to have prior knowledge about the victim and the keyboard.
\item Implement the entire attack in a single C/C++ application. This would make testing and debugging much easier to perform. Instead of requiring several separate tools combined together.
\item Acquire passwords!
\end{enumerate}
